Trends of downward SDR in Thessaloniki

### 2023-04-28 Article.Rmd
Commit 2023-04-28 12:17

```{r trendCLEAR, echo=F, fig.cap="Daily Global radiation seasonal anomaly and long term trend, for clear sky conditions."}
knitr::include_graphics("./images/LongtermTrends-4.pdf")
```

@@

\footnotesize
```{r trendtable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)

pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp <- pp[grep("Global" ,pp$var), ]

pander(pp)
```
\normalsize

@@

>>>>

<!-- ```{r trendCLEAR, echo=F, fig.cap="Daily Global radiation seasonal anomaly and long term trend, for clear sky conditions."} -->
<!-- knitr::include_graphics("./images/LongtermTrends-4.pdf") -->
<!-- ``` -->

@@

\footnotesize
```{r trendtable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("Global" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp) <- NULL
names(pp) <- c("Trend", "Trend p-value", "Sky condition", "Trend statistical significance")

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "Trends of daily means by sky conditions.")
```
\normalsize

@@

\footnotesize
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("Global" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp) <- NULL
names(pp) <- c("Trend", "Trend p-value", "Sky condition", "Season", "Trend statistical sign.")

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "Trends of daily means by sky conditions.")
```
\normalsize
